Spectroscopic confirmation of very-wide stellar binaries and large-separation comoving pairs from \textsl{Gaia DR1}

### 2017-07-29 paper/comoving-followup.tex
caption

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{lamost.pdf}
  \end{center}
  \caption{%
    Stuff
    \label{fig:lamost}}
\end{figure}

>>>>

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{lamost.pdf}
  \end{center}
  \caption{%
    Differences in metallicity and radial velocity for candidate comoving pair
    member stars from the \acronym{LAMOST} survey.
    Points represent each pair, colored by the separation (chord length), and
    error bars represent the uncertainties taken from the \acronym{LAMOST}
    \DR{3} catalog.
    There is a clear over-density of pairs with near-zero differences in
    metallicity and radial velocity even at large ($>1~\pc$) separations, adding
    even more confidence to the existence of comoving star pairs with these
    extreme separations.
    \label{fig:lamost}}
\end{figure}
